---
title: "regioncode: Covert Chinese Regions' Geocode"
author: "Dr.Hu's SRT Team"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
bibliography: vignette.bib
vignette: >
  %\VignetteIndexEntry{regioncode: Covert Chinese Regions' Geocode}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
nocite: |
  @interplot, @Arel-Bundock2018, @DVN/9QZRAD_2020
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(eval = FALSE)
```

Inspired by Vincent Arel-Bundock's well-known `countrycode`,
`regioncode` is an indigenous version for China studies. `regioncode` enables seamlessly converting regions' formal names, common-used names, and geocodes between each other.

## Why `regioncode`?

The Chinese government gives unique geocodes for each county, city, and provincial-level administrative unit. The geocodes were consistently adjusted to matched the national and regional plans of development, taking the new centrally-administered municipality Chongqing (1997) and new state-level new area Xiong'an (2016) as examples. Geocodes adjustment disturb researchers when they try to merge tables which have ddifferent geocodes versions or region id  types. Especially, when researchers render  statistical data on Chinese map, different geocodes between map data and statistical data may cause blank outcomes on plots.


The package is developed to conquer the difficulties to match regional data across years due to such geocodes adjustments. In the current version, `regioncode` enables seamlessly converting Chinese prefecture regions'(named '地级市' in Chinese) formal names, common-used names, and geocodes between each other and across thirty-four years from 1986.

## Installation

To install:

* the latest released version: `install.packages("regioncode")`.
* the latest developing version: `remotes::install_github("sammo3182/regioncode")`.


## Loading Package and Vignetee Data

This example is based on  [`China’s Corruption Investigations Dataset`](https://dataverse.harvard.edu/dataset.xhtml?persistentId=doi:10.7910/DVN/9QZRAD) made by [Yuhua Wang](https://scholar.harvard.edu/yuhuawang/data).

```{r}
# load package
library(regioncode)
# load data
load('vignette_data.rda')
vignette_data <- as.data.frame(vignette_data)
```
```{r eval=FALSE, message=FALSE}
# view data
View(vignette_data)
```
In vignette_data:

- `prefecture_id` means prefecture region administrative geocode
- `prefecture` means prefecture region formal name
- `prefecture_sname` means prefecture region common-used name

## Usage and Arguments

In `regioncode` package, we named regions' geocodes as `code`, regions' formal names as `name`, and regions' common-used names as `sname`.

### Usage
```{r, include=FALSE}
CHNregioncode(
  import,
  year_col,
  from_year,
  to_year = 2015,
  type)
```

### Arguments
- **import**: Table virable that needs geocode coverting.The class of import virable must be dataframe.
- **year_col**: Column that needs to be coverted.
- **from_year**: Code, name or sname version of `year_col`.
- **to_year**: Code, name or sname version you want get. The default is 2015.
- **type**: The function converting type. The Valid strings are: `name2name`, `name2sname`, `name2code`, `code2code`, `code2name`, `code2sname`, `sname2sname`, `sname2name`, and `sname2code`.

## Year Conversion

`regioncode` can covert same region geocodes type into different years from 1986 to 2019.


### Geocodes: `code2code`
```{r}
vignette_covert <- CHNregioncode(import = vignette_data, 
                                 year_col = 'prefecture_id',
                                 from_year = 2019,to_year = 2005,type = "code2code")

```

```{r}
# original geocodes. It's 2019 version
vignette_data$prefecture_id

# after conversion. It's 2005 version
vignette_covert$prefecture_id
```

### Formal Names: `name2name`
```{r}
vignette_covert <- CHNregioncode(import = vignette_data, 
                                 year_col = 'prefecture',
                                 from_year = 2019,to_year = 2005,type = "name2name")
```

```{r}
# original formal names. It's 2019 version
vignette_data$prefecture
# after conversion. It's 2005 version
vignette_covert$prefecture
```

### Common-used Names: `sname2sname`
```{r echo=TRUE}
vignette_covert <- CHNregioncode(import = vignette_data, 
                                 year_col = 'prefecture_sname',
                                 from_year = 2019,to_year = 2005,type = "sname2sname")
```

```{r}
# original common-used names. It's 2020 version
vignette_data$prefecture_sname
# after conversion. It's 2005 version
vignette_covert$prefecture_sname 
```

## Type Conversion
`regioncode` enables seamlessly converting regions' formal names, common-used names, and geocodes between each other.

### From Geocodes to Others: `code2name` and `code2sname`
```{r}
vignette_covert1 <- CHNregioncode(import = vignette_data, 
                                 year_col = 'prefecture_id',
                                 from_year = 2019,to_year = 2005, type = "code2name")

vignette_covert2 <- CHNregioncode(import = vignette_data, 
                                 year_col = 'prefecture_id',
                                 from_year = 2019,to_year = 2005, type = "code2sname")

# original geocodes
vignette_data$prefecture_id
# covert geocodes into formal names
vignette_covert1$prefecture_id
# covert geocodes  into common-used names
vignette_covert2$prefecture_id
```
### From Formal Names to Others: `name2code` and `name2sname`
```{r}
vignette_covert1 <- CHNregioncode(import = vignette_data, 
                                 year_col = 'prefecture',
                                 from_year = 2019,to_year = 2005, type = "name2code")

vignette_covert2 <- CHNregioncode(import = vignette_data, 
                                 year_col = 'prefecture',
                                 from_year = 2019,to_year = 2005, type = "name2sname")

# original formal names.
vignette_data$prefecture
# covert formal names into geocodes
vignette_covert1$prefecture
# covert formal names into common-used names
vignette_covert2$prefecture
```
### From Common-used Names to Others: `sname2code` and `sname2name`
```{r echo=TRUE}
vignette_covert1 <- CHNregioncode(import = vignette_data, 
                                 year_col = 'prefecture_sname',
                                 from_year = 2019,to_year = 2005, type = "sname2code")

vignette_covert2 <- CHNregioncode(import = vignette_data, 
                                 year_col = 'prefecture_sname',
                                 from_year = 2019,to_year = 2005, type = "sname2name")

# original common-used names
vignette_data$prefecture_sname
# covert formal names into geocodes
vignette_covert1$prefecture_sname
# covert formal names into formal names
vignette_covert2$prefecture_sname
```

## Conclusion
The `regioncode` package provide a convenient way to convert Chinese region geocodes, formal names and common-used names between each other. This vignette offers a quick view of package features and a short tutorial for users.

The development of the package is ongoing.The current version only provide Chinese prefecture regions conversion.Out future research promise supporting more administrative level choice, from province level to county level. Please contact us with any questions, bug reports, and comments.

## Affiliation
Yue Hu

Department of Political Science,

Tsinghua University,

Mingzhai 114,

Qinghua Yuan, Haidian District, Beijing 100084, China

Email: yuehu@tsinghua.edu.cn

Website: https://sammo3182.github.io

Dr.Hu's SRT Team

## Reference
